Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-23 article/article.Rmd
Commit 2024-05-23 12:14

We computed the daily trend of the mean OIR of CE <!--
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), --> using a first-order autoregressive
model with a lag of one day, with the 'maximum likelihood' fitting method
[@Gardner1980; @Jones1980] by implementing the function 'arima' from the library
'stats' of the R programming language [@RCT2023]. The trends are reported together
with the $2\sigma$ error.  We observed a negligible change of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
on the mean OIR.
<!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
<!-- knitr::include_graphics("../images/P_daily_trend-1.png") -->
<!-- ``` -->
Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.  Despite the
very weak statistical significance of the mean OIR trend, the annual number of CE
occurrences shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
(Figure\nobreakspace{}\ref{fig:P-energy-N}).
Subsequently, the mean annual energy of the CE events is increasing with a rate of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.  We have to note that the energy related to the CE events can not be
directly linked with the total energy balance of the atmosphere. The net solar
radiation of the region is not increased, but rather redistributed through the CE
events.  This also is depicted by the "instantaneous" values of irradiance (average
over one minute), that can exceed the equivalent clear sky irradiance to a
considerable level.

@@

>>>>

We computed the daily trend of the mean OIR of CE
<!-- (Figure\nobreakspace{}\ref{fig:CEmeanDaily}), -->
using a first-order autoregressive
model with lag of 1 day, with the 'maximum likelihood' fitting method [@Gardner1980;
@Jones1980] by implementing the function 'arima' from the library 'stats' of the R
programming language [@RCT2023]. The trends are reported together with the $2\sigma$
error.  We observe an negligible change of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
on the mean OIR.

<!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
<!-- knitr::include_graphics("../images/P_daily_trend-1.png") -->
<!-- ``` -->

Although, the previous result is closer to the raw data, we preferred to present
the annual statistics, that give a more clear picture about the long term CE
trends. Hence, we calculated the annual values from the one-minute measurements.
Although, the trend of the mean OIR has very weak statistical significance, the
annual number of CE occurrences, shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
(Figure\nobreakspace{}\ref{fig:P-energy-N}).
We have to note that the energy related to the CE events can not be directly
linked with the total energy balance on the atmosphere. The net solar radiation of
the region is not increased, but rather redistributed through the CE events. Resulting,
instantaneous values, that can exceed the equivalent clear sky irradiance to a
considerable level.

@@

Subsequently, the mean annual increase of energy due to CE events is
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.
